A new breeding crossover approach for evolutionary algorithms

### 2023-09-22 paper.tex
Afternoon update.

\abstract*{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. This paper uses the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

\abstract{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

@@

    We propose a new reproduction alternative in this research: a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal. We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation. We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.

    One of the most important contributions of this research is that it proposes a new crossing alternative for the reproduction of individuals in a population. This strategy is practical in evolutionary algorithms where the individual's information has a structure similar to the genetic code's. With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle}, such as Particle Swarm Optimization (PSO).

@@

    To validate our proposal, we performed experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) for evaluation to compare the traditional one-point crossover and our proposed strategy. We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative. These benchmark functions include shifted and rotated versions of traditional benchmark functions (F1-F10), furthermore, there are ten hybrid versions combining the previous functions (F11-F20). The last functions (F21-30) include several compositions of previous benchmark functions, these are the most difficult variants.

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Mathematical benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017).}\label{tab.benchmark_functions}    
    \begin{tabular}{@{}cllcl@{}}
    \toprule
    \multicolumn{5}{c}{\textbf{CEC-2017 Mathematical Benchmark Functions}} \\ \midrule
    \textbf{Fx} & \textbf{Function Name} &  & \textbf{Fx} & \textbf{Function Name} \\
    F1 & Shifted and Rotated   Bent Cigar Function &  & F16 & Hybrid function 6 \\
    F2 & Shifted and Rotated   Sum of Different Power Function &  & F17 & Hybrid function 7 \\
    F3 & Shifted and Rotated   Zakharov Function &  & F18 & Hybrid function 8 \\
    F4 & Shifted and Rotated   Rosenbrock's Function &  & F19 & Hybrid function 9 \\
    F5 & Shifted and Rotated   Rastrigin's Function &  & F20 & Hybrid function 10 \\
    F6 & Shifted and Rotated   Schaffer F7 Function &  & F21 & Composition function   1 \\
    F7 & Shifted and Rotated   Lunacek Bi-Rastrigin's Function &  & F22 & Composition function   2 \\
    F8 & Shifted and Rotated   Non-Continuous Rastrigin's Function &  & F23 & Composition function   3 \\
    F9 & Shifted and Rotated   Levy Function &  & F24 & Composition function   4 \\
    F10 & Shifted and Rotated   Schwefel's Function &  & F25 & Composition function   5 \\
    F11 & Hybrid function 1 &  & F26 & Composition function   6 \\
    F12 & Hybrid function 2 &  & F27 & Composition function   7 \\
    F13 & Hybrid function 3 &  & F28 & Composition function   8 \\
    F14 & Hybrid function 4 &  & F29 & Composition function   9 \\
    F15 & Hybrid function 5 &  & F30 & Composition function   10 \\ \bottomrule
    \end{tabular}
    \end{table}

>>>>

\abstract*{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. This paper uses the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

\abstract{In a previous work, we introduced a population-based, bio-inspired algorithm. The proposed algorithm is inspired by the biological animal life cycle, consisting of the birth, growth, reproduction, and death stages. Our algorithm was initially based on the canonical Genetic Algorithm (GA), where all the individuals have a genotype (chromosome). One difference to highlight in our algorithm is that both the crossing and the mutation are executed through independent processes that randomly affect the population. This paper focuses on breeding, whereas in earlier versions of the algorithm, we used the traditional GA one-point crossover. In this paper, we propose a different alternative to the classical approach, where part of the genetic information is directly copied to each of the offspring in the crossover operator, where this type of crossover may not perform well in continuous optimization problems. In this proposal, we use the parent's genetic information for each gene, using those values as lower and upper bounds of a range, where a random value within that range determines the new value for that gene index of the offspring. This is similar to what is used by algorithms such as Differential Evolution, where we consider our proposal as a variation of existing proposals. We expect this new operator to allow the offspring to continue exploring new search spaces with the birth of individuals. In this paper, we use the benchmark functions introduced in the Competition on Evolutionary Computation for the 2017 edition (CEC-2017) to compare the traditional one-point crossover and our proposed strategy. Experimental results indicate that our proposed operator may be a good alternative for the canonical crossover.}

@@

    We propose a new reproduction alternative in this research: a new breeding crossover approach for evolutionary algorithms using the classic one-point crossover as a reference to our proposal. We performed comparison experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation\cite{awad2016problem} for the 2017 edition (CEC-2017) for evaluation. We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative.

    One of the most important contributions of this research is that it proposes a new crossing alternative for the reproduction of individuals in a population. This strategy is practical in evolutionary algorithms where the individual's information has a structure similar to the genetic code's. With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle,mcdevitt2022particle}, such as Particle Swarm Optimization (PSO).

@@

    To validate our proposal, we performed experiments using the mathematical benchmark functions introduced in the Competition on Evolutionary Computation\cite{awad2016problem} for the 2017 edition (CEC-2017) for evaluation to compare the traditional one-point crossover and our proposed strategy. We finalize with a statistical Z-Test with a ninety-five percent confidence level to determine the best alternative. These benchmark functions include shifted and rotated versions of traditional benchmark functions (F1-F10), furthermore, there are ten hybrid versions combining the previous functions (F11-F20). The last functions (F21-30) include several compositions of previous benchmark functions, these are the most difficult variants.

    We can find a detailed description of the CEC-2017 mathematical benchmark functions, their equations, graphs, and classification in the document \textit{"Problem Definitions and Evaluation Criteria for the CEC 2017 Special Session and Competition on Single Objective Real-Parameter Numerical Optimization"} \cite{awad2016problem}.
